Constraint Programming - Inside Gecode

### 2014-05-06 paper.tex
minor improvements

	\subsection{Search Tree}
	MISSING

	\subsection{Constraint Propagation}
	Constraint propagation is a key concept in constraint programming as it reduces the size of the search space significantly. The term propagation refers in this area to the reduction of domains of variables which are infeasible, considering other constraints and affected variable domains. As the size of the variable domain is related to possibilities which have to be checked by a search, the constraint propagation is able to prune infeasible subtrees. Therefore the whole search process is accelerated.

>>>>

	\subsection{Search Trees}
	MISSING

	\subsection{Constraint Propagation}
	Constraint propagation is a key concept in constraint programming as it reduces the size of the search space significantly. The term propagation refers in this area to the reduction of domains of variables which are infeasible, considering other constraints and affected variable domains. As the size of the variable domain is related to possibilities which have to be checked by a search, the constraint propagation is able to prune complete infeasible subtrees. Therefore the whole search process can be accelerated through constraint propagation.
